Algebraic File Synchronization: Adequacy and Completeness

### 2016-01-03 2015/intro.tex
New title and mentions

In this paper we build on the work done 
on an algebraic approach to synchronization
in \cite{NREC} and add to the theoretical understanding
of synchronization by providing rigorous proofs that the algorithms
we describe work as intended
and offer a solution in our framework that cannot be improved on.

>>>>

In this paper we build on our previous work done 
with Prof. Norman Ramsey
on an algebraic approach to synchronization
(\cite{NREC}),
and add to the theoretical understanding
of synchronization by providing rigorous proofs that the algorithms
we describe work as intended
and offer a solution in our framework that cannot be improved on.

### 2016-01-03 2015/paper.tex
New title and mentions

% fitness, validity, integrity, well-founded
% foundation, groundwork
\title{New Foundations and Fitness of Algebraic File Synchronization}
\author{Elod Pal Csirmaz\\
\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}

@@

I thank Laszlo Csirmaz for his invaluable input on previous drafts of this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.

>>>>

\title{Algebraic File Synchronization: Adequacy and Completeness}
\author{Elod Pal Csirmaz\\
\texttt{\rot{\rot{maz.}{csir}{ep}com}{@}{elod}}}

@@

I thank Laszlo Csirmaz for his invaluable input on this paper,
and Bill Zissimopoulos for his observations on algebraic file synchronization that triggered this research.
